Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-11-23 paper/manuscript.Rmd
Add smth about the trade-offs in the first paragraph of the intro

Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
At a pairwise level, the mutually beneficial relationship between plants and pollinators underpins pollination. 
At a community level, sometimes involving hundreds of species, both plant and pollinator species are connected in a myriad of indirect connections when pollination partners are shared. 
These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferred across the community. 
However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affect the pollination service beyond systems with more than a handful of species. 
Here we investigate how pollinator sharing affects pollen transfer *in natural communities* and how it compares to other factors known to play a role in community dynamics like abundance, traits, and visitation patterns.

>>>>

Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
At a pairwise level, the mutually beneficial relationship between plants and pollinators underpins pollination. 
At a community level, sometimes involving hundreds of species, both plant and pollinator species are connected in a myriad of indirect connections when pollination partners are shared. 
These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferred across the community [@morales_interspecific_2008]. 
Generally speaking, there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affect the pollination service beyond systems with more than a handful of species. 
Here we investigate how pollinator sharing affects pollen transfer *in natural communities* and how it compares to other factors known to play a role in community dynamics like abundance, traits, and visitation patterns.
